# Water flow processes in the unsaturated zone

## Soil water content & suction
Soil moisture and suction head are measured continuously in the field (Figure \@ref(fig:soil-data-field)) and in the forest (Figure \@ref(fig:soil-data-forest)). 
```{r soil-data-field, echo = FALSE, out.width='100%',fig.cap='Matric potential, soil temperature and soil water content measured at 2-3 depths at the field station in Kappelen.'}
sf <- W %>%
  mutate(m..m..Water.Content = ifelse(m..m..Water.Content<=0,NA,m..m..Water.Content),
         m..m..Water.Content.1 = ifelse(m..m..Water.Content.1<=0,NA,m..m..Water.Content.1),
         m..m..Water.Content.2 = ifelse(m..m..Water.Content.2<=0,NA,m..m..Water.Content.2)) %>%
  transmute(Date = Timestamps, 
            WaterContent_10cm_Teros21_. = m..m..Water.Content,
            WaterContent_20cm_HS_. = m..m..Water.Content.1,
            WaterContent_30cm_Teros21_. = m..m..Water.Content.2,
            SoilTemperature_10cm_Teros21_degC = X.C.Soil.Temperature,
            SoilTemperature_30cm_Teros21_degC = X.C.Soil.Temperature.1,
            MatricPotential_10cm_Teros21_kPa = kPa.Matric.Potential,
            MatricPotential_30cm_Teros21_kPa = kPa.Matric.Potential.1) %>%
  pivot_longer(-Date,names_to=c('Parameter','Depth','Sensor','Unit'),values_to='Value',
               names_sep='_')

sf %>%
  drop_na() %>%
  filter(!(Parameter=='WaterContent' & Depth=='10cm')) %>%
  write.table(.,'_bookdown_files/data/Unsaturated_zone_processes/soil_field_data.csv',
              quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

ggplot(sf %>% drop_na()) + 
  theme_bw() + 
  geom_point(aes(Date,Value,color=Depth),size=0.2) + 
  facet_wrap('Parameter', scales = 'free_y', ncol=1, strip.position = 'left', 
             labeller = as_labeller(c(MatricPotential='Matric potential [kPa]', 
                                      SoilTemperature='Soil temperataure [°C]',
                                      WaterContent='Water content [-]'))) + 
  ylab(NULL) + xlab('') + 
  theme(strip.background = element_blank(),
        strip.placement = 'outside')
```

```{r soil-data-forest, echo = FALSE, out.width='100%',fig.cap='Matric potential, soil temperature and soil water content measured at 2-3 depths at the field station in Kappelen.'}
sfo <- read.csv('_bookdown_files/data/data_forest_station.csv', skip=2, sep=',', 
              dec='.')
sfo$Timestamps <- as.POSIXct(sfo$Timestamps, format='%Y-%m-%d %H:%M:%S', tz='CET')
sfo <- sfo %>%
  transmute(Date = Timestamps, 
            WaterContent_10cm_HS_. = m..m..Water.Content,
            WaterContent_20cm_HS_. = m..m..Water.Content.1,
            WaterContent_30cm_HS_. = m..m..Water.Content.2,
            WaterContent_40cm_Teros12_. = m..m..Water.Content.3,
            SoilTemperature_40cm_Teros12_degC = X.C.Soil.Temperature,
            ElCond_40cm_Teros12_mS.cm = mS.cm.Saturation.Extract.EC,
            MatricPotential_10cm_Teros21_kPa = kPa.Matric.Potential,
            SoilTemperature_10cm_Teros21_degC = X.C.Soil.Temperature.1,
            MatricPotential_40cm_Teros21_kPa = kPa.Matric.Potential.1,
            SoilTemperature_40cm_Teros21_degC = X.C.Soil.Temperature.2) %>%
  pivot_longer(-Date,names_to=c('Parameter','Depth','Sensor','Unit'),
               values_to='Value',names_sep='_') 

sfo %>%
  drop_na() %>%
  filter(!(Parameter=='WaterContent' & Depth=='10cm')) %>%
  write.table(.,'_bookdown_files/data/Unsaturated_zone_processes/soil_forest_data.csv',
              quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

ggplot(sfo %>% drop_na() %>%
  filter(!(Parameter=='WaterContent' & Depth=='10cm'))) + 
  theme_bw() + 
  geom_point(aes(Date,Value,color=Depth),size=0.2) + 
  facet_wrap('Parameter', scales = 'free_y', ncol=1, strip.position = 'left', 
             labeller = as_labeller(c(MatricPotential='Matric pot. [kPa]', 
                                      SoilTemperature='Soil temp. [°C]',
                                      WaterContent='Water content [-]',
                                      ElCond='El. cond. [mS/cm]'))) + 
  ylab(NULL) + xlab('') + 
  theme(strip.background = element_blank(),
        strip.placement = 'outside')
```
The sensor measuring water content at 10cm depth in the forest is not working any longer and not displayed here. If you decide to work with the raw data, do not include this sensor in your analysis. The data for the field station is available [here](https://github.com/mabesa/Documentation_GW_field_course_2020/blob/master/_bookdown_files/data/Unsaturated_zone_processes/soil_field_data.csv) and the data for the forest station is available [here](https://github.com/mabesa/Documentation_GW_field_course_2020/blob/master/_bookdown_files/data/Unsaturated_zone_processes/soil_forest_data.csv). 

#### Task 17: Derive a soil-characteristic curve {-}
Use the data linked above to derive soil-characteristic curves for both stations (field and forest). 

## Soil infiltration capacity
Double ring infiltration experiments were done on both, forest and grass soils (Figure \@ref(fig:soil-infiltration-data)). The data presented in Figure \@ref(fig:soil-infiltration-data) is available [here](https://github.com/mabesa/Documentation_GW_field_course_2020/blob/master/_bookdown_files/data/Unsaturated_zone_processes/double_ring_infiltration_data.csv).  

```{r, soil-infiltration-data, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap='3 data sets of soil infiltration data collected on forest and grass ground in Kappelen.'}
sifo1 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_forest1.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifo1 <- sifo1 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifo1) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifo1$`Time-pA` <- as.POSIXct(sifo1$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-pA` <- sifo1$`Time-pA`-sifo1$`Time-pA`[1]
sifo1$`Time-TA` <- as.POSIXct(sifo1$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-TA` <- sifo1$`Time-TA`-sifo1$`Time-TA`[1]
sifo1$`Time-pB` <- as.POSIXct(sifo1$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-pB` <- sifo1$`Time-pB`-sifo1$`Time-pB`[1]
sifo1$`Time-TB` <- as.POSIXct(sifo1$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-TB` <- sifo1$`Time-TB`-sifo1$`Time-TB`[1]

sifo2 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_forest2.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifo2 <- sifo2 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifo2) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifo2$`Time-pA` <- as.POSIXct(sifo2$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-pA` <- sifo2$`Time-pA`-sifo2$`Time-pA`[4349]
sifo2$`Time-TA` <- as.POSIXct(sifo2$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-TA` <- sifo2$`Time-TA`-sifo2$`Time-TA`[4349]
sifo2$`Time-pB` <- as.POSIXct(sifo2$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-pB` <- sifo2$`Time-pB`-sifo2$`Time-pB`[4349]
sifo2$`Time-TB` <- as.POSIXct(sifo2$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-TB` <- sifo2$`Time-TB`-sifo2$`Time-TB`[4349]

sifo3 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_forest3.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifo3 <- sifo3 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifo3) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifo3$`Time-pA` <- as.POSIXct(sifo3$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-pA` <- sifo3$`Time-pA`-sifo3$`Time-pA`[1]
sifo3$`Time-TA` <- as.POSIXct(sifo3$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-TA` <- sifo3$`Time-TA`-sifo3$`Time-TA`[1]
sifo3$`Time-pB` <- as.POSIXct(sifo3$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-pB` <- sifo3$`Time-pB`-sifo3$`Time-pB`[1]
sifo3$`Time-TB` <- as.POSIXct(sifo3$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-TB` <- sifo3$`Time-TB`-sifo3$`Time-TB`[1]

sifi1 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_grass1.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifi1 <- sifi1 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifi1) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifi1$`Time-pA` <- as.POSIXct(sifi1$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-pA` <- sifi1$`Time-pA`-sifi1$`Time-pA`[1]
sifi1$`Time-TA` <- as.POSIXct(sifi1$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-TA` <- sifi1$`Time-TA`-sifi1$`Time-TA`[1]
sifi1$`Time-pB` <- as.POSIXct(sifi1$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-pB` <- sifi1$`Time-pB`-sifi1$`Time-pB`[1]
sifi1$`Time-TB` <- as.POSIXct(sifi1$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-TB` <- sifi1$`Time-TB`-sifi1$`Time-TB`[1]

sifi2 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_grass2.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifi2 <- sifi2 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifi2) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifi2$`Time-pA` <- as.POSIXct(sifi2$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-pA` <- sifi2$`Time-pA`-sifi2$`Time-pA`[1]
sifi2$`Time-TA` <- as.POSIXct(sifi2$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-TA` <- sifi2$`Time-TA`-sifi2$`Time-TA`[1]
sifi2$`Time-pB` <- as.POSIXct(sifi2$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-pB` <- sifi2$`Time-pB`-sifi2$`Time-pB`[1]
sifi2$`Time-TB` <- as.POSIXct(sifi2$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-TB` <- sifi2$`Time-TB`-sifi2$`Time-TB`[1]

sifi3 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_grass3.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifi3 <- sifi3 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifi3) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifi3$`Time-pA` <- as.POSIXct(sifi3$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-pA` <- sifi3$`Time-pA`-sifi3$`Time-pA`[1]
sifi3$`Time-TA` <- as.POSIXct(sifi3$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-TA` <- sifi3$`Time-TA`-sifi3$`Time-TA`[1]
sifi3$`Time-pB` <- as.POSIXct(sifi3$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-pB` <- sifi3$`Time-pB`-sifi3$`Time-pB`[1]
sifi3$`Time-TB` <- as.POSIXct(sifi3$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-TB` <- sifi3$`Time-TB`-sifi3$`Time-TB`[1]

sifo1a <- sifo1[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Forest', Set = 1) 
sifo1b <- sifo1[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Forest', Set = 1) 
sifo1c <- sifo1[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Forest', Set = 1) 
sifo1d <- sifo1[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Forest', Set = 1) 

sifo2a <- sifo2[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Forest', Set = 2) %>%
  filter(Time >= 0)
sifo2b <- sifo2[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Forest', Set = 2) %>%
  filter(Time >= 0) 
sifo2c <- sifo2[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Forest', Set = 2)  %>%
  filter(Time >= 0)
sifo2d <- sifo2[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Forest', Set = 2)  %>%
  filter(Time >= 0)

sifo3a <- sifo3[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Forest', Set = 3) 
sifo3b <- sifo3[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Forest', Set = 3) 
sifo3c <- sifo3[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Forest', Set = 3) 
sifo3d <- sifo3[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Forest', Set = 3) 

sifi1a <- sifi1[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Grass', Set = 1) 
sifi1b <- sifi1[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Grass', Set = 1) 
sifi1c <- sifi1[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Grass', Set = 1) 
sifi1d <- sifi1[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Grass', Set = 1) 

sifi2a <- sifi2[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Grass', Set = 2) 
sifi2b <- sifi2[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Grass', Set = 2) 
sifi2c <- sifi2[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Grass', Set = 2) 
sifi2d <- sifi2[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Grass', Set = 2) 

sifi3a <- sifi3[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Grass', Set = 3) 
sifi3b <- sifi3[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Grass', Set = 3) 
sifi3c <- sifi3[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Grass', Set = 3) 
sifi3d <- sifi3[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Grass', Set = 3) 

si <- full_join(sifo1a,sifo1b,by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo1c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo1d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3d, by = c('Time','Value','Parameter','Unit','Position','Site','Set'))

rm(list=c('sifo1','sifo1a','sifo1b','sifo1c','sifo1d','sifo2','sifo2a','sifo2b',
          'sifo2c','sifo2d','sifo3','sifo3a','sifo3b','sifo3c','sifo3d','sifi1',
          'sifi1a','sifi1b','sifi1c','sifi1d','sifi2','sifi2a','sifi2b','sifi2c',
          'sifi2d','sifi3','sifi3a','sifi3b','sifi3c','sifi3d'))

si %>%
  transmute(Time_seconds_since_start = Time,
            Value = Value,
            Parameter = Parameter,
            Unit = Unit,
            Position = Position,
            Site = Site,
            Data_set = Set) %>%
write.table(.,'_bookdown_files/data/Unsaturated_zone_processes/double_ring_infiltration_data.csv',
            quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

ggplot(si %>% filter(Parameter=='Pressure', Position=='Inner ring') %>% mutate(Set=as.character(Set))) + 
  geom_point(aes(Time/60,Value,color=Set),size=0.2) + 
  facet_wrap('Site') +  
  theme_bw() + ylab('Pressure [bar]') + xlab('Time [minutes since start]') 
```

#### Task 18: Saturated hydraulic conductivity {-}
Calculate the saturated hydraulic conductivity of soil under grass and forest soil.

## Aquifer recharge from precipitation
The daily weather data from the station in Kappelen in given in Figure \@ref(fig:weather-data-Kappelen).  
```{r, weather-data-Kappelen, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, out.width='100%', fig.cap='Daily weather data measured with the IfU weather station in Kappelen and reference evapotranspiration calculated following Penman-Montheith [@Allen1998]. ET0: reference evapotranspiration of short grass in mm, Precip: Daily sum of precipitation in mm, RH: Relative humidity in %, Rs: Daily average solar radiation in MJ/m^2^, Temp: Daily average temperature in °C. Tmin, Tmax: Daily minimum and maximum temperatures in °C, uz: Wind speed at 1.5m above ground.'}
constants <- defaultconstants  # Load default constants from Evapotranspiration package

constants$Elev = coord$`Elevation m a.s.l.`[coord$`Site Name` == 'Soil & weather station field']
constants$lat_rad = coord$`Northing [°]`[coord$`Site Name` == 'Soil & weather station field'] * pi/180
constants$z = 1.5  # m
constants$a_MagnusTetens = 0.611  # kPa
constants$b_MagnusTetens = 17.502  # -
constants$c_MagnusTetens = 240.97  # °C


meteo <- W %>%
  transmute(Year = year(Timestamps),
            Month = month(Timestamps),
            Day = day(Timestamps),
            Hour = hour(Timestamps),
            Minute = minute(Timestamps),
            Precip = mm.Precipitation,  # in mm
            Rs = W.m..Solar.Radiation * (10 * 60) / 1000000,  # in MJ/m2
            uz = m.s.Wind.Speed,  # in m/s
            Temp = X.C.Air.Temperature,  # in deg C
            VP = kPa.Vapor.Pressure)  # in kPa

meteo$VP[meteo$VP > 10] <- NA
meteo <- meteo %>%
  mutate(VPS = constants$a_MagnusTetens * 
           exp((constants$b_MagnusTetens*W$X.C.Air.Temperature)/
                 (constants$c_MagnusTetens+W$X.C.Air.Temperature)),  # in kPa
         RH = VP/VPS*100  # in %
         ) 

meteo_prep <- ReadInputs(varnames = c('Temp','RH','Precip','Rs','uz'), 
                         climatedata = meteo,
                         timestep = 'subdaily',
                         constants = constants, 
                         stopmissing = c(2,2,2),
                         interp_missing_days = F, 
                         interp_missing_entries = T,
                         interp_abnormal = T,
                         missing_method = 'monthly average',
                         abnormal_method = 'monthly average',
                         message = 'no')

meteo_prep$ET0 <- ET.PenmanMonteith(meteo_prep, constants, ts="daily", 
                     solar="data", wind="yes", crop="short", message="no", 
                     AdditionalStats="no", save.csv="no")

# Strictly, missing data should be filled in before calculating averages. In this case, data is nearly complete and error when removing missing data is small. 
meteo_daily <- meteo %>%
  mutate(Date = as.POSIXct(paste(Year,Month,Day,sep='-'),format='%Y-%m-%d')) %>%
  group_by(Date) %>%
  dplyr::summarise(Precip = sum(Precip, na.rm = TRUE),
                   Tmin = min(Temp, na.rm = TRUE),
                   Tmax = max(Temp, na.rm = TRUE),
                   Temp = mean(Temp, na.rm = TRUE),
                   Rs = mean(Rs, na.rm = TRUE),
                   uz = mean(uz, na.rm = TRUE),
                   RH = mean(RH, na.rm = TRUE)) %>%
  drop_na(Date)
meteo_daily$ET0 <- coredata(meteo_prep$ET0$ET.Daily)  

write.table(meteo_daily,'_bookdown_files/data/Unsaturated_zone_processes/daily_ET_Precip_in_mm.csv',
            quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

# meteo %>%
#   mutate(Date = as.POSIXct(paste(Year,Month,Day,sep='-'),format='%Y-%m-%d')) %>%
#   select(-Year,-Month,-Day,-Hour,-Minute) %>%
#   pivot_longer(-Date,names_to='Parameter',values_to='Value') %>%
#   drop_na() %>%
#   ggplot() + 
#   geom_point(aes(Date, Value),size=0.2) + 
#   facet_wrap('Parameter', scale='free_y') + 
#   theme_bw() + 
#   ggtitle('Sub-daily data')

meteo_daily %>% 
  pivot_longer(-Date,names_to='Parameter',values_to='Value') %>%
  ggplot() + 
  geom_point(aes(Date, Value),size=0.2) + 
  facet_wrap('Parameter', scale='free_y') + 
  theme_bw() #+ 
  #ggtitle('Daily data')
```

#### Task 19: Calculate recharge {-}
Calculate groundwater recharge from precipitation using the simplified water balance model:   
Recharge = Precipitation - Evaportranspiration - Runoff    
Note: Assume that surface runoff can be neglected. Pre-computed daily time series of precipitation and evapotranspiration are available [here]('_bookdown_files/data/Unsaturated_zone_processes/daily_ET_Precip_in_mm.csv').    
