# Water flow processes in the unsaturated zone

## Soil water content & suction
Soil moisture and suction head are measured continuously in the field (Figure \@ref(fig:soil-data-field)) and in the forest (Figure \@ref(fig:soil-data-forest)). 
```{r soil-data-field, echo = FALSE, out.width='100%',fig.cap='Matric potential, soil temperature and soil water content measured at 2-3 depths at the field station in Kappelen.'}
sf <- W %>%
  mutate(m..m..Water.Content = ifelse(m..m..Water.Content<=0,NA,m..m..Water.Content),
         m..m..Water.Content.1 = ifelse(m..m..Water.Content.1<=0,NA,m..m..Water.Content.1),
         m..m..Water.Content.2 = ifelse(m..m..Water.Content.2<=0,NA,m..m..Water.Content.2)) %>%
  transmute(Date = Timestamps, 
            WaterContent_10cm_Teros21_. = m..m..Water.Content,
            WaterContent_20cm_HS_. = m..m..Water.Content.1,
            WaterContent_30cm_Teros21_. = m..m..Water.Content.2,
            SoilTemperature_10cm_Teros21_degC = X.C.Soil.Temperature,
            SoilTemperature_30cm_Teros21_degC = X.C.Soil.Temperature.1,
            MatricPotential_10cm_Teros21_kPa = kPa.Matric.Potential,
            MatricPotential_30cm_Teros21_kPa = kPa.Matric.Potential.1) %>%
  pivot_longer(-Date,names_to=c('Parameter','Depth','Sensor','Unit'),values_to='Value',
               names_sep='_')

sf %>%
  drop_na() %>%
  filter(!(Parameter=='WaterContent' & Depth=='10cm')) %>%
  write.table(.,'_bookdown_files/data/Unsaturated_zone_processes/soil_field_data.csv',
              quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

ggplot(sf %>% drop_na()) + 
  theme_bw() + 
  geom_point(aes(Date,Value,color=Depth),size=0.2) + 
  facet_wrap('Parameter', scales = 'free_y', ncol=1, strip.position = 'left', 
             labeller = as_labeller(c(MatricPotential='Matric potential [kPa]', 
                                      SoilTemperature='Soil temperataure [°C]',
                                      WaterContent='Water content [-]'))) + 
  ylab(NULL) + xlab('') + 
  theme(strip.background = element_blank(),
        strip.placement = 'outside')
```

```{r soil-data-forest, echo = FALSE, out.width='100%',fig.cap='Matric potential, soil temperature and soil water content measured at 2-3 depths at the field station in Kappelen.'}
sfo <- read.csv('_bookdown_files/data/data_forest_station.csv', skip=2, sep=',', 
              dec='.')
sfo$Timestamps <- as.POSIXct(sfo$Timestamps, format='%Y-%m-%d %H:%M:%S', tz='CET')
sfo <- sfo %>%
  transmute(Date = Timestamps, 
            WaterContent_10cm_HS_. = m..m..Water.Content,
            WaterContent_20cm_HS_. = m..m..Water.Content.1,
            WaterContent_30cm_HS_. = m..m..Water.Content.2,
            WaterContent_40cm_Teros12_. = m..m..Water.Content.3,
            SoilTemperature_40cm_Teros12_degC = X.C.Soil.Temperature,
            ElCond_40cm_Teros12_mS.cm = mS.cm.Saturation.Extract.EC,
            MatricPotential_10cm_Teros21_kPa = kPa.Matric.Potential,
            SoilTemperature_10cm_Teros21_degC = X.C.Soil.Temperature.1,
            MatricPotential_40cm_Teros21_kPa = kPa.Matric.Potential.1,
            SoilTemperature_40cm_Teros21_degC = X.C.Soil.Temperature.2) %>%
  pivot_longer(-Date,names_to=c('Parameter','Depth','Sensor','Unit'),
               values_to='Value',names_sep='_') 

sfo %>%
  drop_na() %>%
  filter(!(Parameter=='WaterContent' & Depth=='10cm')) %>%
  write.table(.,'_bookdown_files/data/Unsaturated_zone_processes/soil_forest_data.csv',
              quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

ggplot(sfo %>% drop_na() %>%
  filter(!(Parameter=='WaterContent' & Depth=='10cm'))) + 
  theme_bw() + 
  geom_point(aes(Date,Value,color=Depth),size=0.2) + 
  facet_wrap('Parameter', scales = 'free_y', ncol=1, strip.position = 'left', 
             labeller = as_labeller(c(MatricPotential='Matric pot. [kPa]', 
                                      SoilTemperature='Soil temp. [°C]',
                                      WaterContent='Water content [-]',
                                      ElCond='El. cond. [mS/cm]'))) + 
  ylab(NULL) + xlab('') + 
  theme(strip.background = element_blank(),
        strip.placement = 'outside')
```
The sensor measuring water content at 10cm depth in the forest is not working any longer and not displayed here. If you decide to work with the raw data, do not include this sensor in your analysis. The data for the field station is available [here](https://github.com/mabesa/Documentation_GW_field_course_2020/blob/master/_bookdown_files/data/Unsaturated_zone_processes/soil_field_data.csv) and the data for the forest station is available [here](https://github.com/mabesa/Documentation_GW_field_course_2020/blob/master/_bookdown_files/data/Unsaturated_zone_processes/soil_forest_data.csv). 

#### Task 17: Derive a soil-characteristic curve {-}
Use the data linked above, derive curves for both stations (field and forest). 

## Soil infiltration capacity
Double ring infiltration experiments were done on both, forest and grass soils (Figure \@ref(fig:soil-infiltration-data)). The data presented in Figure \@ref(fig:soil-infiltration-data) as well as pressure logs from the outer infiltration ring is available [here](https://github.com/mabesa/Documentation_GW_field_course_2020/blob/master/_bookdown_files/data/Unsaturated_zone_processes/double_ring_infiltration_data.csv).  


```{r, soil-infiltration-data, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap='3 data sets of soil infiltration data collected on forest and grass ground in Kappelen.'}
sifo1 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_forest1.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifo1 <- sifo1 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifo1) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifo1$`Time-pA` <- as.POSIXct(sifo1$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-pA` <- sifo1$`Time-pA`-sifo1$`Time-pA`[1]
sifo1$`Time-TA` <- as.POSIXct(sifo1$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-TA` <- sifo1$`Time-TA`-sifo1$`Time-TA`[1]
sifo1$`Time-pB` <- as.POSIXct(sifo1$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-pB` <- sifo1$`Time-pB`-sifo1$`Time-pB`[1]
sifo1$`Time-TB` <- as.POSIXct(sifo1$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifo1$`Time-TB` <- sifo1$`Time-TB`-sifo1$`Time-TB`[1]

sifo2 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_forest2.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifo2 <- sifo2 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifo2) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifo2$`Time-pA` <- as.POSIXct(sifo2$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-pA` <- sifo2$`Time-pA`-sifo2$`Time-pA`[4349]
sifo2$`Time-TA` <- as.POSIXct(sifo2$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-TA` <- sifo2$`Time-TA`-sifo2$`Time-TA`[4349]
sifo2$`Time-pB` <- as.POSIXct(sifo2$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-pB` <- sifo2$`Time-pB`-sifo2$`Time-pB`[4349]
sifo2$`Time-TB` <- as.POSIXct(sifo2$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifo2$`Time-TB` <- sifo2$`Time-TB`-sifo2$`Time-TB`[4349]

sifo3 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_forest3.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifo3 <- sifo3 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifo3) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifo3$`Time-pA` <- as.POSIXct(sifo3$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-pA` <- sifo3$`Time-pA`-sifo3$`Time-pA`[1]
sifo3$`Time-TA` <- as.POSIXct(sifo3$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-TA` <- sifo3$`Time-TA`-sifo3$`Time-TA`[1]
sifo3$`Time-pB` <- as.POSIXct(sifo3$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-pB` <- sifo3$`Time-pB`-sifo3$`Time-pB`[1]
sifo3$`Time-TB` <- as.POSIXct(sifo3$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifo3$`Time-TB` <- sifo3$`Time-TB`-sifo3$`Time-TB`[1]

sifi1 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_grass1.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifi1 <- sifi1 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifi1) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifi1$`Time-pA` <- as.POSIXct(sifi1$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-pA` <- sifi1$`Time-pA`-sifi1$`Time-pA`[1]
sifi1$`Time-TA` <- as.POSIXct(sifi1$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-TA` <- sifi1$`Time-TA`-sifi1$`Time-TA`[1]
sifi1$`Time-pB` <- as.POSIXct(sifi1$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-pB` <- sifi1$`Time-pB`-sifi1$`Time-pB`[1]
sifi1$`Time-TB` <- as.POSIXct(sifi1$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifi1$`Time-TB` <- sifi1$`Time-TB`-sifi1$`Time-TB`[1]

sifi2 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_grass2.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifi2 <- sifi2 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifi2) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifi2$`Time-pA` <- as.POSIXct(sifi2$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-pA` <- sifi2$`Time-pA`-sifi2$`Time-pA`[1]
sifi2$`Time-TA` <- as.POSIXct(sifi2$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-TA` <- sifi2$`Time-TA`-sifi2$`Time-TA`[1]
sifi2$`Time-pB` <- as.POSIXct(sifi2$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-pB` <- sifi2$`Time-pB`-sifi2$`Time-pB`[1]
sifi2$`Time-TB` <- as.POSIXct(sifi2$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifi2$`Time-TB` <- sifi2$`Time-TB`-sifi2$`Time-TB`[1]

sifi3 <- read.csv('_bookdown_files/data/Unsaturated_zone_processes/Infiltration_grass3.csv', 
                skip = 5, sep=';', na.strings = '#NV',
                colClasses = c('character','numeric','character','numeric',
                               'character','numeric','character','numeric'))
sifi3 <- sifi3 %>%
  select(-starts_with('X')) %>%
  drop_na()
colnames(sifi3) <- c('Time-pA','pA_bar','Time-TA','TA_degC','Time-pB',
                  'pB_bar','Time-TB','TB_degC')
sifi3$`Time-pA` <- as.POSIXct(sifi3$`Time-pA`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-pA` <- sifi3$`Time-pA`-sifi3$`Time-pA`[1]
sifi3$`Time-TA` <- as.POSIXct(sifi3$`Time-TA`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-TA` <- sifi3$`Time-TA`-sifi3$`Time-TA`[1]
sifi3$`Time-pB` <- as.POSIXct(sifi3$`Time-pB`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-pB` <- sifi3$`Time-pB`-sifi3$`Time-pB`[1]
sifi3$`Time-TB` <- as.POSIXct(sifi3$`Time-TB`,format='%d.%m.%Y %H:%M:%OS')
sifi3$`Time-TB` <- sifi3$`Time-TB`-sifi3$`Time-TB`[1]

sifo1a <- sifo1[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Forest', Set = 1) 
sifo1b <- sifo1[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Forest', Set = 1) 
sifo1c <- sifo1[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Forest', Set = 1) 
sifo1d <- sifo1[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Forest', Set = 1) 

sifo2a <- sifo2[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Forest', Set = 2) %>%
  filter(Time >= 0)
sifo2b <- sifo2[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Forest', Set = 2) %>%
  filter(Time >= 0) 
sifo2c <- sifo2[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Forest', Set = 2)  %>%
  filter(Time >= 0)
sifo2d <- sifo2[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Forest', Set = 2)  %>%
  filter(Time >= 0)

sifo3a <- sifo3[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Forest', Set = 3) 
sifo3b <- sifo3[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Forest', Set = 3) 
sifo3c <- sifo3[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Forest', Set = 3) 
sifo3d <- sifo3[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Forest', Set = 3) 

sifi1a <- sifi1[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Grass', Set = 1) 
sifi1b <- sifi1[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Grass', Set = 1) 
sifi1c <- sifi1[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Grass', Set = 1) 
sifi1d <- sifi1[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Grass', Set = 1) 

sifi2a <- sifi2[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Grass', Set = 2) 
sifi2b <- sifi2[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Grass', Set = 2) 
sifi2c <- sifi2[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Grass', Set = 2) 
sifi2d <- sifi2[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Grass', Set = 2) 

sifi3a <- sifi3[,1:2] %>%
  transmute(Time = `Time-pA`, Value = `pA_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Outer ring', Site = 'Grass', Set = 3) 
sifi3b <- sifi3[,3:4] %>%
  transmute(Time = `Time-TA`, Value = `TA_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Outer ring', Site = 'Grass', Set = 3) 
sifi3c <- sifi3[,5:6] %>%
  transmute(Time = `Time-pB`, Value = `pB_bar`) %>%
  mutate(Parameter = 'Pressure', Unit = 'bar', Position = 'Inner ring', Site = 'Grass', Set = 3) 
sifi3d <- sifi3[,7:8] %>%
  transmute(Time = `Time-TB`, Value = `TB_degC`) %>%
  mutate(Parameter = 'Temperature', Unit = 'degC', Position = 'Inner ring', Site = 'Grass', Set = 3) 

si <- full_join(sifo1a,sifo1b,by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo1c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo1d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo2d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifo3d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi1d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi2d, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3a, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3b, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3c, by = c('Time','Value','Parameter','Unit','Position','Site','Set')) %>%
  full_join(., sifi3d, by = c('Time','Value','Parameter','Unit','Position','Site','Set'))

rm(list=c('sifo1','sifo1a','sifo1b','sifo1c','sifo1d','sifo2','sifo2a','sifo2b',
          'sifo2c','sifo2d','sifo3','sifo3a','sifo3b','sifo3c','sifo3d','sifi1',
          'sifi1a','sifi1b','sifi1c','sifi1d','sifi2','sifi2a','sifi2b','sifi2c',
          'sifi2d','sifi3','sifi3a','sifi3b','sifi3c','sifi3d'))

si %>%
  transmute(Time_seconds_since_start = Time,
            Value = Value,
            Parameter = Parameter,
            Unit = Unit,
            Position = Position,
            Site = Site,
            Data_set = Set) %>%
write.table(.,'_bookdown_files/data/Unsaturated_zone_processes/double_ring_infiltration_data.csv',
            quote=FALSE,sep=',',row.names = FALSE,col.names=TRUE)

ggplot(si %>% filter(Parameter=='Pressure', Position=='Inner ring') %>% mutate(Set=as.character(Set))) + 
  geom_point(aes(Time/60,Value,color=Set),size=0.2) + 
  facet_wrap('Site') +  
  theme_bw() + ylab('Pressure [bar]') + xlab('Time [minutes since start]') 
```

#### Task 18: Saturated hydraulic conductivity {-}
Calculate the saturated hydraulic conductivity of soil under grass and forest soil

## Aquifer recharge from precipitation
